Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
Minor changes

%------------------------------------
\subsection{Sampling and Holding in Hybrid Systems}
\label{ssec:SandH}
%------------------------------------

The digital controllers synthesised in this paper are typically used in
closed loops with continuous (and physical) plants.  Thus, the proposed
approach has to consider dynamics of continuous parts of system ({\it e.g.},
plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the
synthesised controller has to consider the issues related to the hybrid
systems studies.

@@

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronized ZOH input and sample and hold output on the plant with
a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse
transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
which can be computed using the following formula:
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, we will use the notation $G(z)$ to represent the
pulse transfer function.
%
\end{mylemma}

@@

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{C_n(z)}{C_d{z}}=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{G_n(z)}{G_d{z}}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
controller's coefficients; similarly $\vec{b}$ and $\vec{a}$ encompass the
plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number
of poles and zeros for the corresponding block.

@@

A typical hybrid system, with a continuous plant and a discrete controller,
is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters
introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the
continuous-time plant model with parametric additive uncertainty $\Delta_p
\vec{G}_s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal,
and $\hat{Y}(z)$ is the output signal affected by the noises and
uncertainties in the closed-loop system.

@@

The ADC and DAC may be abstracted changing the hybrid system in
figure~\ref{fig:sampledsystem} to the digital system in
figure~\ref{fig:digsystem1} where the parametric uncertainties are
represented by $\Delta_p \vec{G}$
%
%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
%
and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
represented as an additive (output) measurement noise $\nu(z)$, thus
$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
obtained reorganizing the equations~\ref{eq:outputfunctions}:
%
\begin{equation}
\label{eq:outputfunctions2}
\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
\end{equation}
%
where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
%
\begin{equation}
\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
\end{equation}

@@

This noise $\nu(z)$ may represent exactly the same effects that $\nu_{1}(z)$
and $\nu_{2}(z)$ represents together.

>>>>

%------------------------------------
\subsection{Sampling and Holding in Closed-loop Systems}
\label{ssec:SandH}
%------------------------------------

The digital controllers synthesised in this paper are typically used in
closed loops with continuous (and physical) plants.  Thus, the proposed
approach has to consider dynamics of continuous parts of system ({\it e.g.},
plant) and discrete parts ({\it e.g.}, digital controller).

@@

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronized ZOH input and sample and hold output on the plant with
a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse
transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
which can be computed using the following formula:
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = \mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, we will use the notation $G(z)$ to represent the
pulse transfer function.
%
\end{mylemma}

@@

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{C_n(z)}{C_d{z}}=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{G_n(z)}{G_d(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
controller's coefficients; similarly $\vec{b}$ and $\vec{a}$ encompass the
plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number
of poles and zeros for the corresponding block.

@@

A typical digital control system system, with a continuous plant and a discrete controller,
is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters
introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the
continuous-time plant model with parametric additive uncertainty $\Delta_p
\vec{G}_s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal,
and $\hat{Y}(z)$ is the output signal affected by the noises and
uncertainties in the closed-loop system.

@@

The ADC and DAC may be abstracted changing the hybrid system in
figure~\ref{fig:sampledsystem} to the digital system in
figure~\ref{fig:digsystem1} where the parametric uncertainties are
represented by $\Delta_p \vec{G}$
%
%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
%
and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
represented as an additive (output) measurement noise $\nu(z)$, thus
%$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
%represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
%obtained reorganizing the equations~\ref{eq:outputfunctions}:
%%
%\begin{equation}
%\label{eq:outputfunctions2}
%\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
%\end{equation}
%%
%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
%%
%\begin{equation}
%\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
%\end{equation}

@@
